Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-07 paper/v1/compilation.tex
adding revisions to paper

The translation from \sysname to RIR is based on a set of rewriting rules.
The first step merges separate constraints. It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by ($\Any \cap \NOT(a)$), where $\Any$ ensures the routes are well-formed.
%
For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Routing} and \CD{Ownership} policies results in the following RIR:

@@

\begin{code}
PG1 \Path \Any \Intersect \End(A)
PG2 \Path \Any \Intersect \End(B)
PL1 \Path \NOT\Enter(\Out) \Intersect \End(E)
PL2 \Path \NOT\Enter(\Out) \Intersect \End(F)
\True \Path \Exit(\Out)
\end{code}

@@

How could such a policy be implemented in BGP? Suppose we set the local preference at router $C$ to prefer $D$ over $E$, and use the BGP MED attribute to influence $W$ to prefer $A$ over $B$. This might work as expected under normal conditions, however, if the A -- C link fails, then suddenly $C$ has made the wrong decision. Traffic will now follow the
$W \cdot B \cdot C \cdot D$ path, even though this path was not specified by the policy. This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy. To make matters worse, the second preference $W \cdot B \cdot C \cdot E$ is available in the network but not being used. This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
We could solve the first problem by placing routes that go through $D$ at $B$, however, we can not fix the second problem---$C$ has made the wrong choice. In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.

>>>>

The translation from \sysname to RIR is based on a set of rewriting rules.
The first step merges separate constraints. It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by ($\Any \cap \NOT(a)$), where $\Any$ ensures the routes are well-formed.
%
For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:

@@

\begin{code}
PG1 \Path \End(A)
PG2 \Path \End(B)
PL1 \Path \textbf{only}(\In) \Intersect \End(E)
PL2 \Path \textbf{only}(\In) \Intersect \End(F)
\True \Path \Exit(\Out)
\end{code}

@@

How could such a policy be implemented in BGP? Suppose we set the local preference at router $C$ to prefer $D$ over $E$, and use the BGP MED attribute to influence $W$ to prefer $A$ over $B$. This might work as expected under normal conditions, however, if the A -- C link fails, then suddenly $C$ has made the wrong decision. Traffic will now follow the
$W \cdot B \cdot C \cdot D$ path, even though this path was not specified by the policy. This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy. To make matters worse, the second preference $W \cdot B \cdot C \cdot E$ is available in the network but not being used. This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
We could solve the first problem by filtering routes that go through $D$ at $B$, however, we can not fix the second problem---$C$ has made the wrong choice. In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.

### 2016-06-07 paper/v1/motivation.tex
adding revisions to paper

Clearly it is no simple task to properly configure even this
small example network manually; devising correct configurations for real networks can quickly become a nightmare. Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several neighbor- or prefix-based exceptions to the default behavior. A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

>>>>

Clearly it is difficult to properly configure even this
small example network manually; devising correct configurations for real networks can quickly become a nightmare. Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several neighbor- or prefix-based exceptions to the default behavior. A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

### 2016-06-07 paper/v2/paper.tex
adding revisions to paper

\usepackage{balance}

@@

\textbf{Abstract---}
We develop a system called \sysname to help network operators with a challenging and error prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex distributed protocols.
%
\sysname allows operators to specify their objectives naturally, describing high-level constraints and preferences on the types of paths that traffic should take through their network or other networks.
%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%
Our compiler automatically translates these specifications to a collection of BGP router configurations.
% that can execute on existing commodity hardware.
%
We introduce data structures and algorithms that guarantee that the compiled, distributed configurations correctly implement the routing policy under all possible combinations of failures.
%
We use \sysname to specify and compile the configurations of real
data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.

@@

Software-defined networking (SDN) and its abstractions
are, in part, the research
community's response to the difficulty of maintaining policy
compliance through distributed device interactions~\cite{ethane}. 
Instead of organizing networks around a distributed 
collection of devices that compute forwarding tables through
mutual interactions, the devices are told how to
forward packets by a centralized controller. The controller is responsible for ensuring that the
paths taken are compliant with operator specifications.
%Researchers
%have developed increasingly sophisticated languages that let operators
%specify desirable network paths~\cite{x,y,z} which are then translated
%to forwarding tables at runtime.

@@

To achieve the second goal, we develop program analysis and compilation
algorithms that translate the regular policies to a graph-based
intermediate representation and from there to per-device BGP configurations, which include various filters and preferences that govern BGP behavior.
%import and export filters, local preferences, MED attributes, and community tags.
We target BGP for pragmatic reasons:
it is a highly flexible routing protocol,
it is an industry standard,
and many networks use it internally as well as externally.
Despite the advent of SDN, many networks will continue to
use BGP for the foreseeable future due to existing infrastructure investments, the difficulty of transitioning to SDN, and the scalability and fault-tolerance advantages of a distributed
control plane.

@@

Consider the backbone network in Figure~\ref{fig:example1}. It has
three neighbors, a customer \CD{Cust}, a peer \CD{Peer}, and a provider \CD{Prov}. The policy of this network is shown on the right. It prefers the neighbors in a certain order (P1) and does not want to act as a transit between \CD{Peer} and \CD{Prov} (P2). It prefers to exchange traffic with \CD{Cust} over \CD{R1} rather than \CD{R2} because \CD{R1} is cheaper (P3). To guard against another AS "hijacking" prefixes owned by \CD{Cust}, the network only sends traffic to a neighbor if \CD{Cust} is on the AS path (P4). Finally, to guard against \CD{Cust} accidentally becoming a transit for \CD{Prov}, it does not use \CD{Cust} for traffic that will later traverse \CD{Prov} (P5).

To implement P1 of the policy, the operators must compute and assign
local preferences such that preferences at \CD{Cust}-facing interfaces
$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
the same time, to satisfy P3 the preference at \CD{R2}'s
\CD{Cust}-facing interface should be lower than that at
\CD{R1}. Implementing P3 properly will require MEDs to be appropriately configured on \CD{R1} and \CD{R2}. 
To implement P2, the operators can assign communities that
indicate where a certain routing announcement entered the
network. Then, \CD{R4} must be configured to not announce to
$\CD{Peer}$ routes that have communities that correspond to the
\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links. Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based import and export filters at each router.

Clearly it is difficult to properly configure even this
small example network manually; devising correct configurations for real networks can quickly become a nightmare. Such networks have many neighbors spanning multiple commercial-relationship classes, differing numbers of links to each neighbor, along with several neighbor- or prefix-based exceptions to the default behavior. A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

@@

To avoid this problem, the operator may decide to disallow "valley" paths, i.e., those that go up, down, and back up again. This guard can be implemented by $X$ and $Y$ rejecting paths through the other. But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{route-aggregation}. If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce \CD{PG} externally. This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.

@@

Policies for (distributed) control planes differ from data-plane
policies in a few important ways. First, control-plane
policies must account for all failures at compile time; there is
no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
%
In \sysname, we enable such specifications through a notion of {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
%
Second, paths in a control-plane policy may be under-specified (e.g.,
"prefer customer" does not indicate a concrete path). The \sysname
compiler treats such under-specifications as constraints on the set of
allowed paths and automatically computes valid sets based on the topology.
%

In the rest of this section, we define \sysname policies for the two 
examples from the previous section, introducing key aspects of
the \sysname language along the way. The complete syntax of the
language as well as our strategy for compiling \sysname policies to
BGP is defined in \S\ref{sec:compilation}.

@@

\sysname allows operators to configure the network with the
abstraction that they have centralized control over routing.
Specifically, the operator simply provides a set of high-level constraints
that describe the 
different routes traffic may (or may not) take and their relative preferences.
\sysname specifications are written modularly via a series
of declarations.
%These definitions allow users to express the three
%major elements of any \sysname specification:  \emph{prefixes},
%\emph{paths} and \emph{policies}.
For example, to begin specification of the backbone
network from the previous section, we first express the idea that for routes leading to our customer,
we prefer using \CD{R1} over \CD{R2} (policy P3 from Figure~\ref{fig:example1}):
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%\end{lstlisting}
\begin{code}
\Define Prefs = \Exit(R1 \Prefer R2 \Prefer Peer \Prefer Prov)
\end{code}
This  statement defines a set of \emph{ranked paths}, which includes
all paths (and only those paths) for which traffic exits our network
through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.  
The paths that exit through \CD{R1}
are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that 
leave through \CD{Peer} and so then \CD{Prov}.  As we
describe in the next section, the \Exit\ predicate, as well as other
path predicates used later in this section, is simply a shorthand for 
a particular regular expression over paths that is expressible in our policy
language.

@@

To associate ranked paths with
one or more prefixes, we define a \sysname \emph{policy}.
Within a policy, statements with the form $t$\Path$p$
associate the prefixes defined by the predicate $t$ with the set of
ranked paths defined by the path expression $p$.  In general,
prefix predicates can be defined by arbitrary boolean combinations
(and, or, not) of concrete prefixes and community tags.  Here,
we assume we have already defined predicates \CD{PCust} for the
customer prefixes.
%and \CD{PInt} for our internal prefixes.
In the following code, ranked paths are associated with
customer prefixes,
and all other prefixes (\CD{true}).\footnote{Policy statements are processed in
order with earlier policy statements taking precedence over later
policy statements.  Hence, when the prefix predicate \True{} follows
the statement involving \CD{PCust}, it is interpreted as
\CD{\True{} \AND{} \NOT{}PCust}.}

@@

\begin{code}
\Define Routing = 
    \{PCust \Path Prefs \AND \End(Cust)
     \True  \Path Prefs \}
\end{code}
\noindent

Line 2 of this policy 
restricts traffic destined to known customer prefixes (\CD{PCust}) to only follow paths that end at the customer. In addition, it enforces the network-wide preference that traffic leaves through \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
%defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
%that connections to the customer through both routers fail,
%a backup route (\CD{\End(Cust)}) is defined that admits traffic along
%any path (including those through other networks) that ends at the customer.
%Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.
Line 3 applies to any other traffic, and allows the traffic to leave through any direct neighbor with the usual preferences of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}. To summarize our progress, the \CD{Routing} policy
implements P1, P3, and P4 from Figure~\ref{fig:example1}.

Since by default routing allows transit traffic (\EG, traffic entering from
\CD{Peer} and leaving through \CD{Prov}), we separately define a
policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
disjunction (\OR) and negation (\NOT) of constraints. 
First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
\begin{code}
\Define transit(X,Y) = \Enter(X \OR Y) \AND \Exit(X \OR Y)
\Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
\end{code}
\noindent
Here we define transit traffic between $X$ and $Y$ as traffic that enters the network through $X$ or $Y$ and then leaves the network through $X$ or $Y$. Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network. Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.

\begin{code}
\Define NoTrans = 
  \{\True \Path \NOT{}transit(Peer,Prov) \AND 
           \NOT{}cust-transit(Cust,Prov)\}
\end{code}
\noindent
The \CD{NoTrans} constraint above requires that all traffic not follow a path that transits the network between \CD{Peer} and \CD{Prov}. Additionally, it prevents traffic from ever following paths that leave our network and later pass through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%
These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failure cases.

@@

\begin{code}
\Define Ownership = 
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)
     \True \Path \End(\Out)\}
\end{code}
\noindent
In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
end at router \CD{A}; traffic matching \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location.
The special keyword \Out{} represents any location outside the user's network, and the keyword \In{} represents any location inside the network.
For the second constraint, we can define another policy:

@@

As before, once \sysname compiles the policy, it is guaranteed to be policy-compliant under all possible failure scenarios. In addition, \sysname will efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.
%It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.

@@

We handle these challenges by breaking compilation into multiple stages and developing efficient algorithms for each (See Figure~\ref{fig:pipeline}). The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation. Vendor-specific adaptors to translate from ABGP to concrete device configurations or to integrate with an existing template-based system are easily added. The \sysname compiler currently generates Quagga configurations by default.

@@

\para{Syntax}
The \sysname FE is just a thin layer atop a core, regular-expression language (RIR) for describing preference-based path constraints. 
Figure~\ref{fig:rir-syntax} shows the RIR syntax. A policy consists of one or more constraints, each of which have a test on the type of route, and a corresponding set of preferred regular paths. Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS. Special \In{} and \Out{} symbols refer to any internal or external location respectively. In addition, $\Sigma$ refers to any symbol. We also use other standard abbreviations
for regular expressions such as $r^+$, which is simply syntactic sugar for $r \cdot r^*$, a sequence of one or more occurrences of $r$, when appropriate.
%% For example, the constraint
%% \[(\textit{prefix}=74.3.28.0/24) \Link \\
%% (as200 \cdot \In^+) \Prefer (as100 \cdot \In^+)
%% \]
%% describes a more-preferred set of paths for traffic announced by a prefix no less specific than \CD{74.125.28.0/24}, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same. The plus operator $\In^+$ stands for $\In \cdot \In^*$, at least one internal hop. Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.

@@

%=====================================================
%
%
%  **Future Work**
%
%
%=====================================================

\section{Future Work}

There are a number of possible directions for future work in programming distributed control planes. One option would be to integrate a model of the environment into the compiler. For example, many ASes make use of informal peering agreements (e.g., tagging routes with certain communities) to enable a wider range of policies. A compiler with this information, could automatically derive routes conforming to these agreements. 
%
Another direction would be to perform policy verification at the level of centralized language. There has been great deal of work on verification of the data plane, but much less so on control plane verification. The \sysname language provides a high-level abstraction of the control plane, which could be amenable to verification or checking equivalence of policies. For example, an operator could check if adding aggregation at various points in the network as an optimization ever changes routing behavior. The automata-based representation of the product graph may lend itself well to this kinds of analysis.
%
While we target BGP in this paper as a distributed backend for \sysname due to its expressiveness, scalability, and uniformity, it should be possible to use other protocols to achieve different types of routing policies (e.g., OSPF). In particular, one could potentially combine different distributed routing protocols through route redistribution to achieve a larger variety of policies.
%
Another possible future direction is automate AS-wide load balancing for BGP. Load-balancing with BGP across external ASes is difficult since there are few mechanisms at the operators disposal. However BGP policies can artificially prepend to the AS path to increases its length, and influence peer decisions. The product graph representation describes, not only which neighbors routers should prefer, but also which neighbors it is indifferent towards. Thus the compiler knowns when it can safely perform load-balancing across different neighbors.

>>>>

@@

\textbf{Abstract---}
We develop a system called \sysname to help network operators with a challenging and error prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex distributed protocols.
%
\sysname allows operators to specify their objectives naturally, describing high-level constraints and preferences on the types of paths that traffic should take through their network or other networks.
%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%
Our compiler automatically translates these specifications to a collection of BGP router configurations.
% that can execute on existing commodity hardware.
%
We introduce data structures and algorithms that guarantee that the compiled, distributed configurations correctly implement the routing policy under all possible combinations of failures.
%
We use \sysname to specify and compile the configurations of real
data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds of routers.

@@

Software-defined networking (SDN) and its abstractions
are, in part, the research
community's response to the difficulty of maintaining policy
compliance through distributed device interactions~\cite{ethane}. Indeed, instead of organizing networks
around a distributed collection of devices that compute forwarding tables through
mutual interactions, the devices are told how to
forward packets by a centralized controller. The controller is responsible for ensuring that the
paths taken are compliant with operator specifications.
%Researchers
%have developed increasingly sophisticated languages that let operators
%specify desirable network paths~\cite{x,y,z} which are then translated
%to forwarding tables at runtime.

@@

To achieve the second goal, we develop program analysis and compilation
algorithms that translate the regular policies to a graph-based
intermediate language and from there to per-device BGP configurations, which include various filters and preferences that govern BGP behavior.
%import and export filters, local preferences, MED attributes, and community tags.
We target BGP for pragmatic reasons:
it is a highly flexible routing protocol,
it is an industry standard,
and many networks use it internally as well as externally.
Despite the advent of SDN, many networks will continue to
use BGP for the foreseeable future due to existing infrastructure investments, the difficulty of transitioning to SDN, and the scalability and fault-tolerance advantages of a distributed
control plane.

@@

Consider the backbone network in Figure~\ref{fig:example1}. It has
three neighbors, a customer \CD{Cust}, a peer \CD{Peer}, and a provider \CD{Prov}. The policy of this network is shown on the right. It prefers the neighbors in a certain order (P1) and does not want to act as a transit between \CD{Peer} and \CD{Prov} (P2). It prefers to exchange traffic with \CD{Cust} over \CD{R1} rather than \CD{R2} because \CD{R1} is cheaper (P3). To guard against another AS "hijacking" prefixes owned by \CD{Cust}, it only sends traffic to them if \CD{Cust} is on the AS path (P4). Finally, to guard against \CD{Cust} accidentally becoming a transit for \CD{Prov}, it does not use \CD{Cust} for traffic that will later traverse \CD{Prov} (P5).

To implement P1 of the policy, the operators must compute and assign
local preferences such that preferences at \CD{Cust}-facing interfaces
$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
the same time, to satisfy P3 the preference at \CD{R2}'s
\CD{Cust}-facing interface should be lower than that at
\CD{R1}. Implementing P3 properly will require MEDs to be appropriately configured. 
To implement P2, the operators can assign communities that
indicate where a certain routing announcement entered the
network. Then, \CD{R4} must be configured to not announce to
$\CD{Peer}$ routes that have communities that correspond to the
\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links. Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based filters at each router.

Clearly it is difficult to properly configure even this
small example network manually; devising correct configurations for real networks can quickly become a nightmare. Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several neighbor- or prefix-based exceptions to the default behavior. A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

@@

To avoid this problem, the operator may decide to disallow "valley" paths, i.e., those that go up, down, and back up again. This guard can be implemented by $X$ and $Y$ rejecting paths through the other. But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{route-aggregation}. If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce the \CD{PG} externally. This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.

@@

Policies for (distributed) control planes differ from data-plane
policies in a few important ways. First, control-plane
policies must account for all failures at compile time; there is
no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
%
In \sysname, we enable such specifications through a notion of {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
%
Second, paths in a control-plane policy may be under-specified (e.g.,
"prefer customer" does not indicate a concrete path). The \sysname
compiler treats such under-specifications as constraints on the set of
allowed paths and automatically computes valid sets based on topology.
%

In the rest of this section, we define \sysname policies for the two 
examples from the previous section, introducing key aspects of
the \sysname language along the way. The complete syntax of the
language as well as our strategy for compiling \sysname policies to
BGP is defined in the next section.

@@

\sysname allows operators to configure the network with the
abstraction that they have centralized control over routing.
Specifically, the operator simply provides a set of high-level constraints
that describe the 
different routes traffic may (or may not) take and their relative preferences.
\sysname specifications are written modularly via a series
of declarations.
%These definitions allow users to express the three
%major elements of any \sysname specification:  \emph{prefixes},
%\emph{paths} and \emph{policies}.
For example, to begin specification of the backbone
network from the previous section, we first express the idea that for routes leading to our customer,
we prefer using \CD{R1} over \CD{R2} (policy P3 from Figure~\ref{fig:example1}):
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%\end{lstlisting}
\begin{code}
\Define ExitCust = \Exit(R1 \Prefer R2)
\end{code}
This  statement defines a set of \emph{ranked paths}, which includes
all paths (and only those paths) for which traffic exits our network
through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
are preferred (\Prefer) to those that exit through \CD{R2}.  As we
describe in the next section, the \Exit\ predicate, as well as other
path predicates used later in this section, is simply a shorthand for 
a particular regular expression over paths that is expressible in our policy
language.

@@

To associate ranked paths with
one or more prefixes, we define a \sysname \emph{policy}.
Within a policy, statements with the form $t$\Path$p$
associate the prefixes defined by the predicate $t$ with the set of
ranked paths defined by the path expression $p$.  In general,
prefix predicates can be defined by arbitrary boolean combinations
(and, or, not) of concrete prefixes and community tags.  Here,
we assume we have already defined predicates \CD{PCust} for the
customer prefixes and \CD{PInt} for our internal prefixes.
In the following code, ranked paths are associated with
customer prefixes, internal prefixes,
and all other prefixes (\CD{true}).\footnote{Policy statements are processed in
order with earlier policy statements taking precedence over later
policy statements.  Hence, when the prefix predicate \True{} follows
statements involving \CD{PCust} and \CD{PInt}, it is interpreted as
\CD{\True{} \AND{} \NOT{}PCust \AND{} \NOT{}PInt}.}

@@

\begin{code}
\Define Routing = 
    \{PCust \Path ExitCust \Prefer \End(Cust)
     PInt  \Path \End(\In)
     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)\}
\end{code}
\noindent
Line 2 of this policy 
defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
that connections to the customer through both routers fail,
a backup route (\CD{\End(Cust)}) is defined that admits traffic along
any path (including those through other networks) that ends at the customer.
Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
inside the user's network and the keyword \Out{} represents any location
outside the user's network.
Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress, the \CD{Routing} policy
implements P1, P3, and P4 from Figure~\ref{fig:example1}.

Since by default routing allows transit traffic (\EG, traffic entering from
\CD{Peer} and leaving through \CD{Prov}), we separately define a
policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
disjunction (\OR) and negation (\NOT) of constraints. 
%union (\Union), intersection (\Intersect), and negation (\NOT) to
%specify the appropriate sets of paths.
%
%% \begin{lstlisting}[mathescape=true]
%% define PP = Peer or Prov
%% define PPTransit = $enter(PP) \AND exit(PP)$
%% define CustTransit = $later(Cust) \AND later(Prov)$

%% define NoTransit = {
%%     $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
%% }
%% \end{lstlisting}
\begin{code}
\Define PP = Peer \OR Prov
\Define PPTrans   = \Enter(PP) \AND \Exit(PP)
\Define CustTrans = \Later(Cust) \AND \Later(Prov)
\Define NoTrans   = \{\True \Path \NOT{}PPTrans \AND \NOT{}CustTrans\}
\end{code}
\noindent
The \CD{NoTrans} constraint above says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}. Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%
These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failure cases.

@@

\begin{code}
\Define Ownership = 
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)
     \True \Path \End(\Out)\}
\end{code}
\noindent
In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
end at router \CD{A}; traffic matching \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location.
For the second constraint, we can define another policy:

@@

As before, once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. \sysname also ensures safety against aggregation-induced black holes.
%It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.

@@

We handle these challenges by breaking compilation into multiple stages and developing efficient algorithms for each (See Figure~\ref{fig:pipeline}). The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation. Vendor-specific adaptors to translate from ABGP to concrete device configurations are easily added to generate concrete configurations.

@@

\para{Syntax}
The \sysname FE is just a thin layer atop a core, regular-expression language (RIR) for describing preference-based path constraints. 
Figure~\ref{fig:rir-syntax} shows the RIR syntax. A policy consists of one or more constraints, each of which have a test on the type of route, and a corresponding set of preferred regular paths. Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS. Special \In{} and \Out{} symbols refer to any internal or external location respectively. In addition, $\Sigma$ refers to any symbol. We also use other standard abbreviations
for regular expressions such as $r^+$, a sequence of one or more occurrences
of $r$, when appropriate.
%% For example, the constraint
%% \[(\textit{prefix}=74.3.28.0/24) \Link \\
%% (as200 \cdot \In^+) \Prefer (as100 \cdot \In^+)
%% \]
%% describes a more-preferred set of paths for traffic announced by a prefix no less specific than \CD{74.125.28.0/24}, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same. The plus operator $\In^+$ stands for $\In \cdot \In^*$, at least one internal hop. Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.

@@
